Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Petersburg version \YellowPaperVersionNumber}}

### 2020-05-11 Paper.tex
Small comment improvement for SAR

&&&& Where $\boldsymbol{\mu}'_{\mathbf{s}}[0]$ and $\boldsymbol{\mu}_{\mathbf{s}}[1]$ (but not $\boldsymbol{\mu}_{\mathbf{s}}[0]$) are treated as two's complement signed 256-bit integers. \\

>>>>

&&&& Where $\boldsymbol{\mu}'_{\mathbf{s}}[0]$ and $\boldsymbol{\mu}_{\mathbf{s}}[1]$ are treated as two's complement signed 256-bit integers, \\
&&&& while $\boldsymbol{\mu}_{\mathbf{s}}[0]$ is treated as unsigned. \\
